Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II \footnote{Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11731009 and 12071011) and LMEQF. Renming Song is supported in part by Simons Foundation (\#429343, Renming Song). Zhenyao Sun is the corresponding author.}

### 2021-02-11 response-ind.tex

\documentclass[12pt,a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage{hyperref}
\usepackage{comment}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\title[Response]{\large Response to the referees' comments}
\begin{document}
	\maketitle	
	We are grateful to the referees for the very helpful comments.
	We have incorporated all the comments made by the referees.
	Here are the changes in response to the comments of the first referee.

@@

	\item ``Page 5: In Lemma 2.1, introduce the notation $\mathcal P^+$;''

	\emph{We replaced ``$h\in \mathcal P^+$'' with ``non-negative $f\in \mathcal P$'' in the Lemma 2.1.}

	\item ``page 6, Lemma 2.4: The same as above: define $x^{1+\beta}$, when $x$ is negative.''

	\emph{In this paper, 
	the non-integer power for negative numbers is not defined. 
	We changed our statement in Lemma 2.4 and added a proof.}

@@

	\emph{Changed as suggested.}

	\item ``page 8: In the first inequality below (2.9), the last part missed $t^{-1}$.''

	\emph{This is a typo. We added $t^{-1}$ back.}

\end{enumerate}
	Here are the changes in response to the comments of the second referee.
	\begin{enumerate}
		\item ``Page 4. line 1. I think that `$\alpha \widetilde \beta \leq \kappa_f b$' should be `$\alpha \tilde \beta > \kappa_f b$'. ''

### 2021-04-23 Proof_AMSE/supCLT-ind-AMSE3.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%            NOTE: The content in this template, including title, authors' name and affiliation, and etc.
%%                 is ONLY a sample for the author's guidance.
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{amse-new}

\numberwithin{equation}{section} %%% Equations numbered by section. If you don't want it, please delete it.

\begin{document}

 \PageNum{1}
 \Volume{201x}{Sep.}{x}{x}
 \OnlineTime{August 15, 201x}
 \DOI{0000000000000000}
 \EditorNote{Received x x, 201x, accepted x x, 201x}

\abovedisplayskip 6pt plus 2pt minus 2pt \belowdisplayskip 6pt
plus 2pt minus 2pt
%%%%%%%%%%%%%%%%
\def\vsp{\vspace{1mm}}
\def\th#1{\vspace{1mm}\noindent{\bf #1}\quad}
\def\proof{\vspace{1mm}\noindent{\it Proof}\quad}
\def\no{\nonumber}
\newenvironment{prof}[1][Proof]{\noindent\textit{#1}\quad }
{\hfill $\Box$\vspace{0.7mm}}
\def\q{\quad} \def\qq{\qquad}
\allowdisplaybreaks[4]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%-------------------       Beginning of  Author's Definitions       -------------------%%
%%                     Note: You may add your own definitions here.

%%-------------------         the end of  Author's Definitions           -------------------%%

\AuthorMark{Surname1 F1. and Surname2 F2. }                             %%%  appear on the head of even pages  %%%

\TitleMark{A Template for Journal}  %%% Running Title, appear on the head of odd pages  %%%

\title{A Template for Journal        %%%   Main Title of your paper  %%%
\footnote{Supported by \ldots (Grant No. \ldots)}}                  %%%   the Fund which you are supported by  %%%

\author{Firstname1 \uppercase{Surname1}}             %%%  1st Author's information   %%%
    {Address\\
    E-mail\,$:$ }

\author{Firstname2 SURNAME2}     %%%  2nd Author's info, if exists, or you may delete this part directly  %%%
    {Address\\
    E-mail\,$:$  }

@@

\Abstract{Please make sure NO reference number in your Abstract since it is misunderstood independent of full text.}      % the abstract

\Keywords{Aaaa, bbbb, cccc}        % the keywords

\MRSubClass{05B05, 05B25, 20B25}      % MR(2000) Subject Classification

@@

\section{Introduction}

\subsection{A Subsection}

Please make sure that your paper contains correct reference
sequence (please resort them according to its {\it alphabetical
order} and make sure that each bibliographical item is labelled
and that these items are recalled using the command
\verb|\cite{...}|, such as \cite{LT}, and \cite{HB,T1,T2,T3})

All equations, theorems, definitions, lemmas, propositions,
corollaries, examples, remarks etc. would be better to be numbered
consecutively and unrepeatedly within each section. For example,
Definition 2.1, Lemma 2.2, Theorem 2.3 \ldots.

Use \verb|\label| and \verb|\ref| or \verb|\eqref| to
automatically cross-reference sections, equations, theorems and
theorem-like environments, tables, figures, etc.

\begin{theorem}[\cite{HB}]\label{th:1.1} %Theorem 1.1 could be recalled by using Theorem \ref{th:1.1}
The statements of theorems, lemmas, definitions, propositions,
corollaries, conjectures, etc. are set in italics, by using
\begin{verbatim}
\begin{theorem/lemma/definition/proposition/corollary/conjecture}
\end{theorem/lemma/definition/proposition/corollary/conjecture}.
\end{verbatim}
\end{theorem}

\begin{prof}  %you can also use the environment \begin{proof}\end{proof}
Observe that
\begin{align}\label{E:1.1}
AAAAAAAAAA &= BBBBBBBBBBB\nonumber \\
           &\quad + CCCCCCCCCC\nonumber \\
           &= DDDDDDDDDDDDD.
\end{align}
Now apply induction on $n$ to \eqref{E:1.1}\ldots
\end{prof}

\begin{remark}\label{re:1.2}
Remarks, examples, problems, etc. are set in roman type.
\end{remark}

\subsection{Table}

\begin{table}
\begin{tabular}{|c|c|c|l|c|}
\hline $P(x)$ & $i$& $(e(1),e(2),e(4))$ & $(e(3),e(6),e(12),e(24))$ & $T(E)$ \\
\hline $P_1$  &    & & &$\emptyset$ \\
\hline $P_2$  & 4  & & $(1,1,1,0)\rightarrow(0,0,0,1)$ &2\\
\hline $P_3$  & 2  & &$(1,1,1,0)\rightarrow(0,0,2,0)$ &1\\
\hline $P_4$  & 2  & $(0,1,1)\rightarrow(1,2,0)$ & &1\\
\hline $P_5$  & 2  & $(0,1,1)\rightarrow(1,2,0)$ &$(1,1,1,0)\rightarrow(0,0,0,1)$ &$1,2$\\
\hline $P_6$  & 6  & $(0,1,1)\rightarrow(1,2,0)$ &$(1,1,1,0)\rightarrow(2,2,0,0)$ &1\\
\hline $P_7$  & 3  & $(0,1,1)\rightarrow(1,0,1)$ &$(1,1,1,0)\rightarrow(2,0,1,0)$ &0\\
\hline $P_8$  & 3  & $(0,1,1)\rightarrow(2,1,0)$ &$(1,1,1,0)\rightarrow(2,0,1,0) \rightarrow(3,1,0,0)$ &$0,1$\\
\hline
\end{tabular}
\caption{Aaa bbb ccc\label{tab}}
\end{table}

\subsection{Figure}

%\centerline{\includegraphics[scale=1.2]{actmark.eps}}
%\centerline{\small Figure 1\quad Journal mark}

\acknowledgements{\rm We thank the referees for their time and
comments. }

>>>>

\documentclass{amse-new}
%%---------- Beginning of Author's packages --------%%
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
%%---------- the end of Author's packages ----------%%
\numberwithin{equation}{section}
\begin{document}
 \PageNum{1}
 \Volume{201x}{Sep.}{x}{x}
 \OnlineTime{August 15, 201x}
 \DOI{0000000000000000}
 \EditorNote{Received x x, 201x, accepted x x, 201x}
\abovedisplayskip 6pt plus 2pt minus 2pt \belowdisplayskip 6pt
plus 2pt minus 2pt
\def\vsp{\vspace{1mm}}
\def\th#1{\vspace{1mm}\noindent{\bf #1}\quad}
\def\proof{\vspace{1mm}\noindent{\it Proof}\quad}
\def\no{\nonumber}
\newenvironment{prof}[1][Proof]{\noindent\textit{#1}\quad }
{\hfill $\Box$\vspace{0.7mm}}
\def\q{\quad} \def\qq{\qquad}
\allowdisplaybreaks[4]
%%-------------------       Beginning of  Author's Definitions       -------------------%%
\theoremstyle{definition}
\newtheorem{asp}{Assumption}
%%-------------------         the end of  Author's Definitions           -------------------%%

\AuthorMark{Ren Y.-X., Song R., Sun Z. and Zhao J.}
\TitleMark{Stable CLT for super-OU processes, II}

\title{Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes, II
\footnote{Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11731009 and 12071011) and LMEQF. Renming Song is supported in part by Simons Foundation (\#429343, Renming Song). Zhenyao Sun is the corresponding author.}}

\author{Yan-Xia \uppercase{Ren}}             %%%  1st Author's information   %%%
    {LMAM School of Mathematical Sciences \& Center for Statistical Science, Peking University, \\
	    Beijing 100871, P. R. China \\
    E-mail\,$:$ yxren@math.pku.edu.cn}

    \author{Renming \uppercase{Song}} 
    {Department of Mathematics, University of Illinois at Urbana-Champaign, \\
  	Urbana, IL 61801, USA\\
    E-mail\,$:$ rsong@illinois.edu}

    \author{Zhenyao \uppercase{Sun}} 
    {School of Mathematics and Statistics, Wuhan University, \\
  	Wuhan, Hubei 430072, P. R. China \\
	Faculty of Industrial Engineering and Management, Technion, \\
	Haifa 3200003, Israel\\
    E-mail\,$:$ zhenyao.sun@gmail.com}

    \author{Jianjie \uppercase{Zhao}} 
    {School of Mathematical Sciences, Peking University,\\
  	Beijing 100871, P. R. China\\
    E-mail\,$:$ zhaojianjie@pku.edu.cn}

@@

\Abstract{
	This paper is a continuation of our recent paper (Electron. J. Probab. \textbf{24} (2019), no. 141) and is devoted to the asymptotic behavior of a class of supercritical super Ornstein-Uhlenbeck processes $(X_t)_{t\geq 0}$ with branching mechanisms of infinite second moment.
	In the aforementioned paper, we proved stable central limit theorems for  $X_t(f) $ for {\it some} functions $f$ of polynomial growth in three different regimes.
	However, we were not able to prove central limit theorems for $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
	In this note, we show that the limiting stable random variables in the three different regimes are independent, and as a consequence, we get stable central limit theorems for  $X_t(f) $ for {\it all} functions $f$ of polynomial growth.
}

\Keywords{Superprocesses, Ornstein-Uhlenbeck processes, stable distribution, central limit theorem, law of large numbers, branching rate regime}

\MRSubClass{60J68, 60F05}

@@

\section{Introduction and main result}
\label{subsec:M}
	Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
	Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
\begin{align}
  	Lf(x)
  	= \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
  	\quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
\end{align}
	where $\sigma > 0$ and $b > 0$ are constants.
	Let $\psi$ be a function on $\mathbb R_+$ of the form
\begin{align}
  	\psi(z)
  	=- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(\mathrm dy),
  	\quad  z \in \mathbb R_+,
\end{align}
	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2)\pi(\mathrm dy)< \infty$.
	$\psi$ is referred to as a branching mechanism and $\pi$ is referred to as the L\'evy measure of $\psi$.
	Denote by $\mathcal M(\mathbb R^d)$ ($\mathcal M_c(\mathbb R^d)$) the space of all finite Borel measures (of compact support) on $\mathbb R^d$.
	Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ ($\mathcal B(\mathbb R^d, \mathbb R_+)$) the space of all $\mathbb R$-valued ($\mathbb R_+$-valued)
	Borel functions on $\mathbb R^d$.
	For $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\mu(f)= \int f(x)\mu(\mathrm dx)$ and $\langle f, g\rangle = \int f(x)g(x) \mathrm dx$ whenever the integrals make sense.
	We say a real-valued Borel function $f$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if, for each $t\in \mathbb R_+$, we have $ \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty. $
	For any $\mu \in \mathcal M(\mathbb R^d)$, we write $\|\mu\| = \mu(1)$.
	For any $\sigma$-finite signed measure $\mu$, denote by $|\mu|$ the total variation measure of $\mu$.

	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a \emph{$(\xi, \psi)$-superprocess}, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{align}
  	\label{eq: def of V_t}
  	\mathbb{P}_{\mu}[e^{-X_t(f)}]
  	= e^{-\mu(V_tf)},
   	\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{align}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{align}
  	V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) ) \mathrm ds\Big]
	= \Pi_x [f(\xi_t)],
	\quad x\in \mathbb R^d, t\geq 0.
\end{align}	
	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses,Li2011Measure-valued} for instance.

	There have been many central limit theorem type results for branching processes, branching diffusions and superprocesses, under the second moment condition.
	See \cite{AdamczakMilos2015CLT, AsmussenHering1983Branching, Athreya1969Limit,Athreya1969LimitB,Athreya1971Some, Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved, KestenStigum1966Additional,KestenStigum1966A-limit,Milos2012Spatial,RenSongZhang2014Central,RenSongZhang2014CentralB, RenSongZhang2015Central,RenSongZhang2017Central}.
	For a detailed literature review, see \cite[Section 1.1]{RenSongSunZhao2019Stable}.
	There are also  central  limit theorem type results for supercritical branching processes and branching Markov processes with branching mechanisms of infinite second moment.
	For earlier papers, see \cite{Asmussen76Convergence, Heyde1971Some}. 	
	Recently, Marks and 
	%Milo\'s
	Mi{\l}o\'s
	\cite{MarksMilos2018CLT} established some spatial central limit theorems for supercritical branching OU processes with a special stable offspring distribution.
	In \cite{RenSongSunZhao2019Stable}, we established stable central limit theorems for super-OU processes $X$ with branching mechanisms $\psi$ satisfying the following two assumptions.

\begin{asp}[Grey's condition]
\label{asp: Greys condition}
	There exists $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$ and  $\int_{z'}^\infty \psi(z)^{-1} \mathrm dz < \infty$.
\end{asp}

\begin{asp}
\label{asp: branching mechanism}
  	There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{align}
    \int_{(1,\infty)}y^{1+\beta +\delta}\Big|\pi(\mathrm dy)-\frac{\eta \mathrm dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty
\end{align}
	for some $\delta > 0$.
\end{asp}

	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
$
	D
	:=\{\exists t\geq 0~\text{such that}~ \|X_t\| =0 \}
$
	is non-trivial with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$.
	It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.
    Throughout this paper, $\beta$ and  $\eta$ always stand for the constants in
     Assumption \ref{asp: branching mechanism}.

	We now recall some notation and basic facts from \cite{RenSongSunZhao2019Stable}.
	We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
	Define $P^{\alpha}_t f(x) := e^{\alpha t} P_t f(x) = \Pi_x [e^{\alpha t}f(\xi_t)]$ for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	It is known that $\mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)$ for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	The OU process $\xi$ has an invariant probability on $\mathbb R^d$:
\begin{align}
  	\varphi(x)\mathrm dx
  	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx.
\end{align}
	Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{align}
  	\langle f_1, f_2 \rangle_{\varphi}
  	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) \mathrm dx, \quad f_1,f_2 \in L^2(\varphi).
\end{align}
	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
		The eigenfunctions of $L$
		consists of
		a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
For each $p\in \mathbb Z_+^d$,
$\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$, where $|p|:= \sum_{k=1}^d p_k$.
	For each function $f\in L^2(\varphi)$, define the order of $f$ as
$\kappa_f
  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}$
with the convention that $\inf\emptyset=\infty.$

	For $p\in \mathbb{Z}_+^d$, define
$H_t^p
    	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.$
	For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
	We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that
	for any
	$\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
	Furthermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
We will write $H^0_t$ and $H^0_\infty$ as $H_t$ and $H_\infty$, respectively.

	Denote by $\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
$\mathcal{P}
  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.$
	Define
	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \},
		~
	\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
	$ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
	Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
	Define a semigroup
\begin{align}\label{e:Tt}
	T_t f
	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
	\quad t\geq 0, f\in \mathcal P,
\end{align}
	and a family of functionals
\begin{align}\label{eq:M.13}
	m_t[f]
	:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx,
	\quad 0 \leq t< \infty, f\in \mathcal P.
\end{align}
	Let us recall the definition of the non-integer power of complex numbers here.
	For each $z\in \mathbb C\setminus (-\infty, 0]$, we define $\log z : = \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined so that $z = |z|e^{i \arg z}$.
	For each $z\in \mathbb C\setminus (-\infty, 0]$ and $\gamma \in \mathbb R$, we define $z^\gamma := e^{\gamma \log z}$.
	For each $\gamma \geq 0$, we define $0^\gamma := \lim_{z\to 0, z\in \mathbb C\setminus (-\infty,0]} z^\gamma=\mathbf 1_{\gamma = 0}$.

	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
\begin{equation} \label{eq:I:R:3}
\begin{minipage}{0.9\textwidth}
	for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,$ where
\begin{equation}
	m[f]
	:=
\begin{cases}
	\lim_{t\to \infty} m_t[f], &
	f \in \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l, \\
	\lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l.
\end{cases}
\end{equation}
\end{minipage}
\end{equation}
		For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
	We also proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
\begin{equation}\label{eq:oldResult}
\begin{minipage}{0.9\textwidth}
	if $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb {\widetilde P}_\mu$,
\[
\begin{split}
	&e^{-\alpha t}\|X_t\| \xrightarrow[t\to \infty]{\text{a.s.}} \widetilde{H}_\infty;
	\quad \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s};
	\\&\frac{X_t(f_\mathrm c)}{\|t X_t\|^{1-\tilde \beta} } \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm c};
	\quad\frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
	\xrightarrow[t\to \infty]{d} \zeta^{-f_\mathrm l},
\end{split}
\]
	where $\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
	$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; and
\[
	\mathrm x_t(f)
	:= \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty},
	\quad t\geq 0, f\in \mathcal P.
\]
\end{minipage}
\end{equation}
	Any  $f \in \mathcal P$ can be decomposed as
	$f=f_s + f_c + f_l$
	with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$.
	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem for $f$ if  $\|f_\mathrm s\|_{L^2(\varphi)}> 0, \|f_\mathrm c\|_{L^2(\varphi)} = 0$ and $\|f_\mathrm l\|_{L^2(\varphi)}> 0$.
	We conjectured there that the limit random variables in \eqref{eq:oldResult} for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
	Once this asymptotic independence is established, a central limit theorem  for $ X_t(f)$ for all $f\in  \mathcal P$ would follow.

	The main purpose of this note is to show that the limit  random variables in \eqref{eq:oldResult} are independent.

\begin{theorem}
\label{thm:M}
	If $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb {\widetilde P}_\mu$,
\begin{align} \label{eq:M.1}
	&S(t):=
	\Bigg(e^{-\alpha t}\|X_t\|, \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}}, \frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
	\Bigg)
	\\&\xrightarrow[t\rightarrow \infty]{d}(\widetilde H_\infty,\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}),
\end{align}
	where $\mathrm x_t(f_\mathrm l)$ is defined in
	\eqref{eq:oldResult}
	with $f$ replaced with $f_\mathrm l$;
	$\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
	$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3};
	$\widetilde H_\infty$,  $\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
\end{theorem}

	As a corollary of this theorem, we get  central limit theorems for $X_t(f)$ for all $f\in \mathcal P$.

\begin{corollary}
	Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P$.
	Let  $f=f_\mathrm s + f_\mathrm c + f_\mathrm l$ be the unique decomposition of $f$ with $f_\mathrm s \in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$.
	Then under $\widetilde {\mathbb{P}}_{\mu}$, it holds that
\begin{enumerate}
\item
	if $f_\mathrm c\equiv 0$, then
\[
    \frac{ X_t(f) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l},
\]
	where $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are independent;
\item
if $f_\mathrm c\not\equiv 0$, then
\[
    \frac{ X_t(f) - \mathrm x_t(f)}{\|tX_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d}
   \zeta^{f_\mathrm c},
\]
	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variable described in \eqref{eq:I:R:3}.
\end{enumerate}
\end{corollary}

\begin{remark}
	We mention here that  the branching mechanism $\psi$ considered in this paper can be written in a form of $\psi(z)= -\alpha z + z^{1+\beta} (\eta + \epsilon(z))$ where $\epsilon (z) \to 0$ as $z \to 0$ (See \cite[Remark 1.3]{RenSongSunZhao2019Stable}).
	It would be interesting to consider the more general cases $\psi(z)= -\alpha z + z^{1+\beta}l(z)$ where $l(z)$ is only assumed to be a slowly varying function.
For this more general case, the arguments of \cite{RenSongSunZhao2019Stable} and this paper no longer work. It seems that new idea and treatment are needed.
\end{remark}

\section{Proof of main result}
\label{proofs of main results}
	We first make some preparations before proving Theorem \ref{thm:M}.
	For every $t\geq 0$ and $f\in \mathcal P$, define
\[
  	Z_t f
  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
  	\quad \Upsilon^f_t
   	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
\]
From
	\cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of
the weak limit of $\Upsilon^f_t$.
	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
	The following Lemma \ref{lem:P:R} can be proved using
an argument similar to that used in the proof of
	\cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
\begin{lemma}
\label{lem:P:R}
	For any $g\in \mathcal P$ there exists non-negative $h \in \mathcal P$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
\end{lemma}

	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable},
with Lemma \ref{lem:P:R} replacing the role of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}.
	Let $(\mathscr F_t)_{t\geq 0}$ be the natural filtration of $X$.
	\begin{proposition}
\label{thm:Key}
	For any $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
\[
	\mathbb P_\mu
	\Big[ \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  \big|\Big]
	\leq C e^{- \delta t}.
\]
\end{proposition}

	The following generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable} will be used later in the proof of  Theorem \ref{thm: II}, a special case of Theorem \ref{thm:M}.
	Note that the constants $C$ and $\delta$ in the next result depend only on $f,g\in \mathcal P$ and $\mu\in \mathcal M_c(\mathbb R^d)$, do not depend on $n_1, n_2, f_j, g_j$ and $t$ (as long as $t\geq n_1+1$).
